AA: The Algorithmic Autoregulation (Distributed Software Development) Methodology

### 2013-06-02 front-matter.tex
mudado titulo
arrumados vinculos da autoria

\title{
AA Distributed Software Development Methodology
}

@@

\author[1,3]{Renato Fabbri\thanks{renato.fabbri@gmail.com}}
\author[2,3]{Ricardo Fabbri\thanks{rfabbri@iprj.uerj.br}}
\author[1,3]{Vilson Vieira\thanks{vilson@void.cc}}
\author[3]{Alexandre Negr\~{a}o}
\author[3]{Lucas Zambianchi}
\author[3]{Marcos~Mendon\c{c}a}
\author[1,3]{Daniel Penalva}
\author[3]{Danilo Shiga}
\affil[1]{\small Physics Insitute at S\~{a}o Carlos (IFSC), University of S\~{a}o Paulo (USP), Brazil}
\affil[2]{\small Polytechnic Institute (IPRJ), State University of Rio de Janeiro (UERJ), Nova Friburgo, Brazil}
\affil[3]{\small \url{LabMacambira.sourceforge.net}}

>>>>

\title{
    AA: The Algorithmic Autoregulation (Distributed Software Development) Methodology
}

@@

\author[1,4]{Renato Fabbri\thanks{renato.fabbri@gmail.com}}
\author[2,4]{Ricardo Fabbri\thanks{rfabbri@iprj.uerj.br}}
\author[1,4]{Vilson Vieira\thanks{vilson@void.cc}}
\author[4]{Alexandre Negr\~{a}o}
\author[4]{Lucas Zambianchi}
\author[4]{Marcos~Mendon\c{c}a}
\author[1,3]{Daniel Penalva}
\author[4]{Danilo Shiga}
\affil[1]{\small Physics Insitute at S\~{a}o Carlos (IFSC), University of S\~{a}o Paulo (USP), S\~ao Carlos, Brazil}
\affil[2]{\small Polytechnic Institute (IPRJ), State University of Rio de Janeiro (UERJ), Nova Friburgo, Brazil}
\affil[3]{\small  Institute for Theoretical Physics (IFT), Universidade Estadual Paulista (UNESP), S\~ao Paulo, Brazil}
\affil[4]{\small \url{LabMacambira.sourceforge.net}}
